Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & Chi^2 &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & Chi^2 &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}

@@

Concern &  Responses &  Frequency &   \\
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 186 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\

>>>>

\usepackage{url}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | c | c | c |}
Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & $\chi^2$ &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & $\chi^2$ &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}

@@

Concern &  Responses &  Frequency   \\
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 186 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
